---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fdatest

<!-- badges: start -->
[![R-CMD-check](https://github.com/permaverse/fdatest/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/permaverse/fdatest/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of fdatest is to implement various statistical methods for domain
selection in functional data analysis, that is selecting a subset of the domain
where the difference between two populations is significant. The package is
based on the paper by Abramowicz et al. (2022) and Pini & Vantini (2017).

## Installation

You can install the package from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("fdatest")
```

Alternatively, You can install the development version of fdatest from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("permaverse/fdatest")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fdatest)

# Performing the TWT for two populations on the NASA temperatures data set
withr::with_seed(1234, {
  out <- TWT2(NASAtemp$paris, NASAtemp$milan)
})

# Plotting the results of the TWT
plot(
  out, 
  xrange = c(0, 12), 
  main = 'TWT results for testing mean differences'
)
```
